A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-06-07 manuscript.Rmd
reformat code chunk

```{r, include=FALSE}
knitr::write_bib(c(.packages(), "repro", "here", "rticles", "gert", "bookdown", "lavaan", "knitr", "targets", "renv", "tidyverse"),
                 "packages.bib")
```

>>>>

```{r, include=FALSE}
knitr::write_bib(
  c(
    .packages(),
    "repro",
    "here",
    "rticles",
    "gert",
    "bookdown",
    "lavaan",
    "knitr",
    "targets",
    "renv",
    "tidyverse"
  ),
  "packages.bib"
)
```
